---
title: "<center> <h1>Proposal</h1> </center>"
author: "<center> <h4> STAT 420 / Francis Galton Group Project</h4> </center>"
date: "<center> <h6>07/02/2018 </h6> </center>"
output:
  html_document:
    number_sections: no
    theme: united
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: 2
---
```{r setup, include=FALSE}
options(knitr.kable.NA = '')
library(knitr)
library(kableExtra)
library(gridExtra)
library(dplyr)
library(plyr)
library(devtools)
library(MASS)
library(ggplot2)
library(lmtest)
library(lattice)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=10, fig.height=5) 
#options("scipen"=0, "digits"=7)
#options(scipen = 999)
```

```{r, echo = FALSE}
mydf = read.csv("fhs.csv")
dic = read.csv("dictionary.csv")
```

### Team
- Joerg Heintz, NetID: jheintz
- Japson Jeyasekaran, NetID: japsonj2

### Background

The data set is from the Framingham Heart Study, which is a long-term, ongoing cardiovascular cohort study on residents of the city of Framingham, Massachusetts. The study began in 1948 with 5,209 adult subjects from Framingham, and is now on its third generation of participants. The main goal of that study is to extend the body knowledge concerning heart diseases.  

- Framingham Study: https://www.framinghamheartstudy.org/  
- Data Source: https://courses.edx.org/courses/HarvardX/PH207x/2012_Fall/datasets/  

The Francis Galton team is interested in analyzing health data to extend a physician’s diagnostic expertise and decision making by generating and providing “actionable intelligence”. Therefore we investigated the influence of education and gender on heart diseases. 


### Variables

The data set contains `r dim(mydf)[1]` records and `r dim(mydf)[2]` variables of the types integer, numeric, and factor. Please find a brief explanation below in the scollable table.   

```{r, echo = FALSE}

kable(dic) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "bordered"), full_width = T, position = "center")   %>%
  row_spec(0, bold = T, color = "white", background = "dodgerblue") %>%
        scroll_box(width = "100%", height = "200px")  

```



### Data Set
```{r,  fig.width= 8, fig.height= 8, echo = FALSE}
data = mydf[complete.cases(mydf), ]

kable(data[1:200,]) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "bordered"), full_width = T, position = "center")   %>%
  row_spec(0, bold = T, color = "white", background = "dodgerblue") %>%
        scroll_box(width = "100%", height = "200px")  

```



### Report Structure

- Introduction
- Methods
- Results
- Discussion
- Appendix


**George & Japson, July 15**




